---
title: "Multiple factor analysis package"
author: "Dan Shen, Letian Shi, Xin Wang, Qianyi Yang, Yue You"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
## Package Info
This package provides functions to analyze and visualize multiblock data sets using multiple factor analysis.

## How to use the package

Here is an example to illustrate how to use this package
```{r}
source("../R/mfa.r")
source('../R/plot.r')
source('../R/method.r')
source('../R/print.r')
source('../R/bootstrap.r')
```
###Read the data from file(You may change the path)
```{r}
data_raw<-read.csv("../../data/wines.csv")
#Pick the useful part
data<-data_raw[,2:54]
#Make a list store the block division
pick1<-list(seq(1,6),seq(7,12),seq(13,18),seq(19,23),seq(24,29),
            seq(30,34),seq(35,38),seq(39,44),seq(45,49),seq(50,53))
col_name<-names(data)
pick2<-list(col_name[1:6],col_name[7:12],col_name[13:18],col_name[19:23],col_name[24:29],
            col_name[30:34],col_name[35:38],col_name[39:44],col_name[45:49],col_name[50:53])
```

###Construct the object 
```{r}
review<-mfa(data,pick1)
```
### print method
```{r}
print.mfa(review)
```
### plot method
```{r}
plot.mfa(review, dim_plot=c(1,2), cex=0.8, mfrow=c(5,2))
```
### Additional method to analyse the MFA object
####1.summary_eigen
```{r}
test1<-summary_eigen(review)
```
####2.contribution
```{r}
test2<-contribution(review,type="observation")
test3<-contribution(review,type="variable")
test4<-contribution(review,type="table")
```
####3.RV
```{r}
num_block<-length(review$weight)
test5<-RV(review$scale_x[,seq(review$divide[1],review$divide[2]-1)],
          review$scale_x[,seq(review$divide[num_block-1],review$divide[num_block]-1)])
```
####4.LG
```{r}
test6<-LG(review$scale_x[,seq(review$divide[1],review$divide[2]-1)],
          review$scale_x[,seq(review$divide[num_block-1],review$divide[num_block]-1)])
```
####5. Bootstrap
```{r}
bootstrap_ratio = bootstrap.mfa(review, 10)
```
